Updated Constraints on Self-Interacting Dark Matter from Supernova 1987A

### 2017-05-10 draft.tex
Wrote a brief conclusion section.

We have revisited constraints on SIDM models in which the 
self-interaction arises from dark electromagnetism. We have 
constrained the mixing parameter for models in which the dark photon 
mixes with the standard model photon through a kinetic mixing term.

>>>>

We have revisited constraints on SIDM models in which the 
self-interaction arises from dark electromagnetism. We have 
constrained the mixing parameter for models in which the dark photon 
mixes with the standard model photon through a kinetic mixing term. Our calculation 
is similar to previous work in Ref.~\cite{dent_etal12} and Ref.~\cite{rrapaj_reddy16} and 
is aimed at clarifying some confusion in the literature on this subject that may stem 
from several errors in the calculation of Ref.~\cite{dent_etal12}.

Our constraints are on the mixing parameter are shown in 
Fig.~\ref{fig:constraint} and agree well with the those presented in 
Ref.~\cite{rrapaj_reddy16} and, for dark photon masses $m_{\mathrm{A}'} \gtrsim 10$~MeV, 
Ref.~\cite{hardy_lasenby17}. We argue that the lower bound on the dark photon mixing parameter 
is only sensitive to the SRA to within a factor of $\sim 3$ or less. A more precise constraint 
on such models from SN1987A is probably not practicable because the interior temperature 
of the SN1987A core is somewhat uncertain and this uncertainty alone gives rise to an uncertainty 
in the excluded region of at least a factor of $\sim 2-3$. Finally, \citet{hardy_lasenby17} consider 
plasma effects within the supernova. The most important ramification of this work in the context of 
our paper is that it suggests significantly weaker constraints on $\varepsilon$ in the mass 
range $m_{\mathrm{A}'} \lesssim 10$~MeV.
